Unifying intraspecific and interspecific variation in tropical tree mortality

### 2016-07-19 ms/supp.Rnw
Format for supplementary materials
- layout for title etc
- add figures
- add references to figure in main text

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} = Template for a one-column mathematics article
% {pnasinvited} = Template for a PNAS invited submission

\title{Unifying intraspecific and interspecific variation in tropical tree mortality}

@@

% Please give the surname of the lead author for the running footer
\leadauthor{Camac}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Add something significant here}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{J.C. designed and performed the analysis; D.F. conceived the idea, supervized the development of this work; S.J.W \& M.W. provided biological insight. All authors contributed to the writing of this manuscript.}

\authordeclaration{The authors declare that they have no competing financial interests.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: james.camac@gmail.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Tropical trees $|$ wood density $|$ growth $|$ mortality $|$ interspecific}

\begin{document}
% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalized the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

\subsection*{Modelling true growth}

@@

\subsection*{Mortality model}
\subsection*{Model fitting}
Our observations are for survival outcomes $S_{i, t_2\rightarrow t_3}$ (0 = alive, 1 = died) for each individual $i$ between censuses at time $t_2$ and $t_3$. We model these observations as random realizations from a Bernoulli distribution
\begin{equation}
S_{i,t_2\rightarrow t_3} \sim \textrm{Bernoulli}(p_{i,t_2\rightarrow t_3}),
\end{equation}
where $p_{i,t_2\rightarrow t_3}$ is the probability individual $i$ dies in the interval $t_2$--$t_3$ *(eq. \ref{eq:mortality_model}). As we only have a point estimate of $\lambda_i(t)$ at $t=t_2$, the cumulative hazard from  $t_2$--$t_3$ is approximated as
\begin{equation}
  \int_{t_2}^{t_3} \lambda_i(t) {\rm d}t \approx \lambda_i(t_2) (t_3-t_2).
\end{equation}

@@

>>>>

\documentclass[9pt,onecolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\templatetype{pnasresearcharticle}

\title{
{\normalfont \fontsize{12pt}{16pt}
{\color{black50} Supporting information for:}\\} \vskip6pt
\fontsize{16pt}{20pt} Unifying intraspecific and interspecific variation in tropical tree mortality
}

@@

\dates{This supplement was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\hypersetup{
     linkcolor=pnasbluetext
}

\RequirePackage[colorlinks=true, allcolors=blue]{hyperref}

\begin{document}

\maketitle

\tableofcontents

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{secnumdepth}{0}

\section{Appendix A - Supplementary text}

Example reference \cite{Johnson-2016}.

<<preload, echo=FALSE>>=
n_inds <- as.character(round(nrow(BCI_model_dataset_true_unique),-2))
n_spp <- length(unique(BCI_model_dataset_true_unique$sp))
proportion_negative <- round(nrow(subset(BCI_model_dataset_true_unique, obs_dbh_dt<0))/nrow(BCI_model_dataset_true_unique)*100)
n_obs_errors <- nrow(BCI_dbh_error_data$discrep)
obs_error_sigma <- round(sd(BCI_dbh_error_data$discrep),2)
n_heldout <- as.character(nrow(BCI_training_sets[[1]]$heldout))
@

\subsection{Modelling true growth}

@@

\subsection{Mortality model}
Our observations are for survival outcomes $S_{i, t_2\rightarrow t_3}$ (0 = alive, 1 = died) for each individual $i$ between censuses at time $t_2$ and $t_3$. We model these observations as random realizations from a Bernoulli distribution
\begin{equation}
S_{i,t_2\rightarrow t_3} \sim \textrm{Bernoulli}(p_{i,t_2\rightarrow t_3}),
\end{equation}
where $p_{i,t_2\rightarrow t_3}$ is the probability individual $i$ dies in the interval $t_2$--$t_3$ *(eq. \ref{eq:mortality_model}). As we only have a point estimate of $\lambda_i(t)$ at $t=t_2$, the cumulative hazard from  $t_2$--$t_3$ is approximated as
\begin{equation}
  \int_{t_2}^{t_3} \lambda_i(t) {\rm d}t \approx \lambda_i(t_2) (t_3-t_2).
\end{equation}

@@

\clearpage
\section{Appendix 2 - Example stan code}

Include example model here

Describe how to get other models?

\clearpage
\section{Supplementary Figures}

\begin{figure}[!hb]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{figures/supp_fig1}
\caption{ About this figure}
\label{figS1}
\end{figure}

\clearpage
\begin{figure}[!hb]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{figures/supp_fig2}
\caption{ About this figure}
\label{figS2}
\end{figure}

\clearpage

\section{References}

\bibliography{refs.bib}
\end{document}
